Ecological network control

### 2018-06-08 paper/manuscript.Rmd
Add results of controllability models
Close #13

The size of the minimum driver node set relative to the number of species in each network $n_D$ ranged between `r round(min(c_m$n_D), 2)` and `r round(max(c_m$n_D), 2)` (mean `r round(mean(c_m$n_D), 2)`, Figure \@ref(fig:fig-emp-controllability)).

```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/sqrt(2), fig.cap="Density plot ofsize of the minimum driver node set. The vertical dashed line indicates the meann value."}
drake::loadd(fig_emp_controllability)
fig_emp_controllability
```

>>>>

The size of the minimum driver node set relative to the number of species in each network $n_D$ ranged between `r round(min(c_m$n_D), 2)` and `r round(max(c_m$n_D), 2)` (mean `r round(mean(c_m$n_D), 2)`, Figure \@ref(fig:fig-emp-controllability)). 
We found this not to be related to any of the evaluated metrics. 
The most parsimonious model, as determined by the AICc was the null model, which included not predictors (Supplementary Information \@ref(S-controllability-models)).

```{r fig-emp-controllability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/2, fig.cap="Density plot ofsize of the minimum driver node set. The vertical dashed line indicates the meann value."}
drake::loadd(fig_emp_controllability)
fig_emp_controllability
```

### 2018-06-08 paper/supp-info.Rmd
Add results of controllability models
Close #13

>>>>

# Controllability models {#controllability-models}

The models were

```{r}
drake::loadd(controllability_models)

replace_terms <- function(x){
  x %>% 
    stringr::str_replace("inv", "inv") %>%
    stringr::str_replace("connectance", "C") %>%
    stringr::str_replace("weighted_NODF", "NODF") %>%
    stringr::str_replace("n_sp", "n_s") %>%
    stringr::str_replace("web_asymmetry", "AS_n") %>%
    stringr::str_replace("interaction_strength_asymmetry", "AS_s") %>%
    stringr::str_replace(stringr::fixed("~"), "\\sim ")
}

AICcmodavg::aictab(controllability_models) %>% 
  dplyr::mutate(Modnames = replace_terms(Modnames)) %>% 
  dplyr::select(Modnames, AICc, Delta_AICc, Cum.Wt) %>%
  dplyr::filter(Delta_AICc <= 8) %>%
  dplyr::rename(model = Modnames, `$\\Delta AICc$` = Delta_AICc, `$AICc$` = AICc, `Cum. Weight` = Cum.Wt) %>%
  dplyr::mutate(model = paste0("$", model, "$")) %>% 
  knitr::kable(escape = FALSE, 
               booktabs = TRUE, 
               digits = 2, 
               linesep = c(""),
               caption = "Model selection table based on the Akaike Information Criterion for small samples for candidate models of size of the minimum driver node set ($n_D$) in the empirical networks. There was no evidence for any of the evaluated predictors: the invasion status (inv), the network connectance (C), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$). Only candidate models with $\\Delta AIC < 8$ are shown.")
```
